Persistence of marine populations under climate and fishing

### 2014-03-03 Writing/MS.tex
emmas comment on line 104

Regardless of the exact functional form of the recruitment function, the critical parameter in determining population persistence is how quickly recruitment increases when the population size is near (but above) $0$, which is equivalent to the intrinsic growth rate $R_0=f'(0)$.  For each kernel, the population's ability to persist depends on properties of the population itself -- the expected distance a larva disperses $\langle d \rangle$ and the intrinsic growth rate $R_0$; properties of the environment -- the length of the viable patch $L$ and how quickly the environment shifts $c$; and the harvesting rate $h$.  
%% A little confusing. First you say that the critical parameter for persistence is equivalent to the intrinsic growth rate, and then list a bunch of other parameters that are also important for determining it. 
For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that

>>>>

Regardless of its exact functional form, the only property of the recruitment function that determines whether or not a population can persist is how quickly recruitment increases when the population size is near (but above) $0$, which is equivalent to the intrinsic growth rate $R_0=f'(0)$.  For each kernel, therefore, the population's ability to persist depends on properties of the population itself -- the expected distance a larva disperses $\langle d \rangle$ and the intrinsic growth rate $R_0$; properties of the environment -- the length of the viable patch $L$ and how quickly the environment shifts $c$; and the harvesting rate $h$.  
For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that
